Agile Methods and Model Driven Engineering: a survey

### 2017-12-08 article.tex
Pre-Final version of the paper.

\lettrineabstract{Model Driven Engineering together with its synonymous is an approach to Software Engineering, which promotes the usage of abstract model as primary assets during the development process. Concrete software artifacts can be generated from models with few to none human interaction. It has its origin academia and has been adopted from industrial consortiums.
Agile is another approach, which has arisen in the practice of Software Engineering. It describes a set of values and principles for software development under which requirements and solutions iteratively evolve through the collaborative effort of self-organizing cross-functional teams. The idea is to put the individual and its interactions over fixed plans and schedules.
Both approaches have been considered to be contradicting. Indeed this paper reveals that there is not much material available, which consider a combination of both. Though there exists evidence that both approaches can be combined. This requires an adaption of the approaches with respect to the other but also yield promising positive results.
}
%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section{Introduction}

% Really nice looking first letter
%\lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.

TODO FAHI write the intro %TODO FAHI

\section{Method}

@@

Answers to these questions will help us to understand, if both approaches to Software Engineering are used in combination in practice, if their combination yields positive effects and in what areas it is actually applied. 
To get profound results we are looking for peer-reviewed scientific publications published in journals or conferences. 
We decided incorporate the following databases for our search:
\begin{itemize}
\item ACM Digital Library
\item Google Scholar
\item IEEExplore
\item ScienceDirect
\end{itemize}

@@

The search yielded around thirty results in the ACM and IEEE library and more than 3000 results in the two other databases. 
We decided to restrict the time interval to papers after 2001 as the \emph{Agile Manifesto} \cite{secondaryAgileManifesto} was published in this year, which can be considered to be the beginning of the Agile movement.
To narrow the search further down, we defined the following inclusion criteria:
\begin{description}
\item[Inclusion] conference or journal article, contains practical relevance, papers after 2001
\end{description}

We applied this criteria by looking at title and abstract of the discovered results. 
It turned out that most of the found papers did not contain Agile and MDE methodology at the same time.
Furthermore a lot of papers did not refer to any practical experiences.
After rigorously applying the filter criteria we ended with 13 papers. 
For the analysis we did not apply a fixed review protocol due to the size of the found material.
A survey about discovered result is presented in the next section.

\section{Survey}

%TODO FAHI, FFO, JOB wrtie their summary
\subsection{Agile Model Driven Development}

Modeling is an important part of all software development projects because it enables to think through complex issues before the attempt to address them via code. This is true for agile projects, for not-so-agile projects, for embedded projects, and for business application projects. Unfortunately, many modeling efforts prove to be dysfunctional. At one end of the spectrum there are projects where no modeling is performed, either because the developers haven’t any modeling skills or because they have abandoned modeling as a useless endeavor. At the other end of the spectrum there are projects which sink in a morass of documentation and overly detailed models, either because the project team suffers from “analysis paralysis” and finds itself unable to move forward or because the team has burdened itself with too many modeling specialists who don’t have the skills to move forward even if they wanted to. Somewhere in the middle, there are project teams that invest in modeling and documentation efforts only to discover that the programmers ignore the models anyway, often because the models are unrealistic or simply because the programmers think they know better than the modelers (and often they do). The goal of Agile Model Driven Development (AMDD) is to show how to avoid these problems, to gain the benefits of modeling and documentation without suffering the drawbacks \cite{1}.

AMDD as the agile version of MDD (Model Driven Development) takes a much more realistic approach: its goal is to describe how developers and stakeholders can work together cooperatively to create models which are just barely good enough. It assumes that each individual has some modeling skills, or at least some domain knowledge, that they will apply together in a team in order to get the job done. It is reasonable to assume that developers will understand a handful of the modeling techniques out there, but not all of them. It is also reasonable to assume that people are willing to learn new techniques over time, often by working with someone else that already has those skills.

@@

S. W. Ambler \cite{2} believes that modeling is a way to think issues through before the code step because it lets to think at a higher abstraction level. One can also do this by writing a test before writing functional code, along the lines of test-driven development.
With the Agile Model Driven Development (AMDD) approach, one typically do just enough high-level modeling at the beginning of a project to understand the scope and potential architecture of the system, and then during development iterations modelling will be done as part of the iteration planning activities to. In this way light models will be done in several minutes as precursor to several hours of coding.

@@

In the end of \cite{2} there is a discussion between Axel Uhl and Scott W Ambler, Axel remarks some projects where MDA succeeded nevertheless Scott answers saying that he is not very excited about MDA due to big failures of some projects in the past.

@@

This article \cite{3} presents the concept of Agile Model Driven Development or AMDD as an attempt to effectively bring together the fast pace of agile development and the guaranteed quality of model-driven development. This methodology makes use of the strong contrast between Agility and Model Driven Software Engineering or MDSE, attempting to cover each of their flaws with the strong points of the other, creating a symbiotic association. For instance, MDSE strict focus on documentation and models generation can supply perfectly the documentation “phobia” that suffers agile development.

@@

The final statement is that although AMDD is a promising field in a research and practical context, the author considers it not mature at all, stressing that it is still in its “infancy”. This paper can be used as an starting point in a AMDD research for creating, adapting or selecting AMDD processes.

@@

This paper \cite{4} provides an overview on the practice of Agile Modeling Method Engineering or AMME. This practice mixes the use of modeling and agile methodologies, as a way to evolve modeling requirements all along the software life cycle and to connect more stakeholders and developers.

@@

Burden et.\,al. \cite{10} empirically investigate three companies, namely \emph{Ericson AB}, \emph{Volvo Cars} and \emph{Volvo Group}, which undergo a parallel shift to MDE and Agile Methods concerning their development methodologies.
They contribute to the broad empirical study by Hutchinson et. al. \cite{secondaryHutchinsonEmpirical} about the use of MDE in industry.
In general their observations validate the findings of Hutchinson et. al., e.\,g. MDE works best in narrow well-understood domains, it has to be driven bottom-up through developers and must be put on the critical path.
Though, they also refute some of the previous findings: 
Engineers are actually well-trained in MDE methodology by universities, code gurus appreciate code generators to reduce repetitive tasks, middle managers welcome MDE as it help minimizing risks and architects might find the complexity of MDE tools intimidating.
As a result Agile and MDE can yield synergies:
Agile profits from MDE by the enforced integration of stakeholders by abstracting away from the actual implementation and by reducing external dependencies because outsourced activities are brought back in-house through automation.
The success from MDE can profit from the bottom-up approach of Agile Methods.
A further interesting finding of \cite{10} is the importance of secondary tools. 
As MDE tools again can cause repetitive tasks, engineers naturally develop secondary tools, e.\,g. scripts to again automate this activities.

@@

In \cite{11} Kulkarni et.\,al. report about their experiences on the introduction of Agile Methods in a MDE based software development process within \emph{Tata Consultancy Services}.
This company is specialized on the delivery of E-commerce solutions for a wide range of customers from different areas.
As their customers require individual solutions but with common requirements between customers, MDE turned out to be very effective as a majority of an application can be generated and only minor adjustments are required.
The development of their MDE platform used to be based on a traditional plan-driven approach. 
When they changed to an agile approach, they first suffered a loss of productivity and estimations were always wrong. 
After a few weeks, the process stabilized and they actually experienced an significant improvement of productivity and accuracy of estimates.
However, they experienced that a pure agile approach is not adequate for MDE, as sometimes in-depth analysis, exploration and research might be required in the development of the MDE tools.
As Agile promotes the delivery of executable artifacts and short timely intervals, these kinds of activities are barely feasible.
Therefore they adapted their approach by introducing Meta-Sprints, i.\,e. a longer sprint which is allowed to produced non-executable artifacts such as documentation, proof-of-concept prototypes etc.
Kulkarni et. al. really positive experiences with these adapted agile approach.

@@

Golra et.\,al. \cite{12} report on their experience about using Agile Methods for the development of Domain Specific Languages in a project for a governmental organization in France.
In spite of defining the language top down with strict semantics, they developed metamodel, model and graphical representations in parallel with loose coupling in between the artifacts.
They identified several positive finding on the effects of Agile within MDE.
Agile Methods within the development of graphical DSLs is a success story as it facilitates communication with domain experts and development requires flexibility both in tools and communication.
However, the authors point out that further conceptual studies in this area are required.

@@

This paper is the initial paper in a proposed series of publications that sets the stage for the research to be conducted by the authors. The authors have identified gaps in the corpus of knowledge of the field of agile model driven development. They have identified gaps in 1) the understanding of the state of practice of agile model driven development 2) the benefits that agile MDD is supposed to provide and 3) identifying the challenges that beset the adoption of agile MDD \cite{alfraihi2016towards}.

The authors begin by describing Model Driven Development as a new paradigm where models are the main artefact in software development and from which code is generated. They describe agile development as an approach that imposes a disciplined project management structure upon software development. To the authors, both MDD and Agile methods share a core aim of accelerating the development process yet their approaches to achieve this aim are different.

@@

To the authors, agile model driven development is an attempt to get the best of both paradigms while mitigating their drawbacks. To achieve this, significant research needs to be conducted to address the gaps identified. There is also a brief section on related work where a review of the current research in agile model driven development is presented. This literature review shows that most of the current work in the field is aimed at classifying how agile and MDD approaches are combined. The authors point out that none of the published literature in the field addresses the questions of benefits and challenges of agile MDD \cite{matinnejad2011agile,stavru2013challenges,whittle2014state}.

@@

In this paper, a case study is presented where agile model driven development approaches are applied to the development of a real time telecommunications system at Motorola \cite{zhang2011agile}. In this case study, the investigators combined system-level agile process (SLAP) and an MDD process into one to speed up development rate, improve product quality and shorten delivery cycle time. SLAP is an agile process adopted at Motorola that uses scrum as a baseline and includes certain extreme programming practices. SLAP divides a software development life cycle into multiple iterations. Each iteration consists of three sprints: application requirements and architecture, development, and system integration feature testing (SIFT). Each sprint is five weeks long and has the same set of activities (called its calendar).

@@

SLAP divides a software development life cycle into multiple iterations. Each iteration consists of three sprints: application requirements and architecture, development, and system integration feature testing (SIFT). Each sprint is five weeks long and has the same set of activities (called its calendar).

@@

\begin{description}
\item[Limited support for distributed development environments:] software. Documentation and models should be created and maintained only if they provide value to the project and project stakeholders. Otherwise, face-to-face communication is as important in distributed environments as the non-distributed environment.
\item[Limited support for subcontracting:] The process may be an iterative, incremental approach, but the subcontractor may have to make the process predictive by specifying the number of iterations and the deliverables of each iteration in order to compete.
\item[Limited support for building reusable artifacts:] While there seems to be a case for applying agile processes to the development of reusable artifacts, it is not clear how agile processes can be suitably adapted.
\item[Limited support for development involving large teams:] There may be opportunities for teams to use agile practices, but the degree of agility possible may be less than that found in smaller projects.
\item[Limited support for developing safety-critical software:] it can be assumed that agile and formal software development are not incompatible but can be combined when needed: Formal techniques may be used in an agile way to handle critical pieces of the software to increase quality and confidence.
\item[Limited support for developing large, complex software:] The assumption that code refactoring removes the need to design for change may not hold for large complex systems in particular. The complexity and size of such software may make strict code refactoring costly and error-prone. Models can play an important role here, especially if tools exist for generating significant portions of the code from the models. This view of models as the central artifacts for evolving systems is at the heart of the Object Management Group’s (OMG) Model-Driven Architecture (MDA) approach.
\end{description}

@@

Two case studies where conducted on the engineering teams responsible for the clutch control for the electrical drivetrain in a hybrid vehicle and for the active high beam highlight. Both case studies implemented MDE and agile methods in the workflow. The studies indicate that the development cycle where shortened by implementing the new methods in the engineering teams, but that one of the biggest problem to address is the faulty plant models delivered from the third party vendors. The paper concludes with that MDE and agile methods can successfully be combined to speed up the development phase of a software system in a car. With faster feedback methods from the agility framework, the developers were able to address holes in their knowledge and decrease the number of errors in their preliminary software. The paper also suggested more future work with MDE methods, and more automated code generation.

@@

Rivero et. al. \cite{RIVERO2014670} introduces a bottom-up driven approach on implementing model-driven web engineering. Instead of using the traditional top-down approach in model-driven engineering, where application content is modeled initially, the authors suggest to invert the development process and start with the user interface-mockups. From the mockups, code generation and model-driven engineering methods are used to build the actual functional software. By inverting the normal top-down approach normally found in MDE, the authors argue that the result is an agile prototype-based iterative process, with the advantages of automatic code-generation and documentation from MDE.

The paper concludes that their method reduces the errors and effort in model building, while at the same time allows introducing agile features to the modeling process. By generating code based on mockups, the authors method shows a fast and agile way of developing user friendly web application, where non domain-experts can create functional web design straight from they’re conceptualized mockups. For future work the authors will keep testing and validating the developed tool by using it to build applications. They are also extending the tool to provide code generation capabilities for common Web technologies and architectures.

\section{Conclusion}

This section summarizes the results of the survey and present the conclusion extracted.
Despite the survey covered the study of just 13 papers, good results and relevant information were found.

@@

Accordingly to the reports we found during the research, projects that eventually incorporated or followed AMDD improved the results in some way.
The study case of Volvo Car Group revealed that MDE and agile methods can successfully be combined to speed up the development phase of a software system in a car\cite{Eliasson2014}.
Rivero et. al. \cite{RIVERO2014670} showed that by generating code based on mockups, the authors method shows a fast and agile way of developing user friendly web application, where non domain experts can create functional web design straight from their conceptualized mockups.
The results in the case of Motorola \cite{zhang2011agile} declared that 93\% of the entire component code was automatically generated and the quality of the automatically generated code in terms of defects density was significantly higher than manual code.

>>>>

\lettrineabstract{Model Driven Engineering is an approach to Software Engineering, which promotes the usage of abstract model as primary assets during the development process. Concrete software artifacts can be generated from models with few to none human interaction. It has its origin in academia and has been adopted from industrial consortiums.
Agile is a different approach, which arose in the practice of Software Engineering. 
It describes a set of values and principles for software development under which requirements and solutions iteratively evolve through the collaborative effort of self-organizing cross-functional teams. 
Both approaches have been considered to be contradicting. 
Indeed this paper reveals that there are only few resources available reporting about a combination of both. 
Though, this paper reveals evidence that both approaches can be combined. 
On the one hand this imposes further challenges as it requires an adaption of the approaches with respect to the other but on the other hand also yields promising positive results.
}
%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section{Introduction}
\label{sec:intro}

Software Engineering is "the application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software" \cite{IEEEglossary}.
Over the past decades there have been several of those approaches on how to best develop and evolve software systems. 
In this paper we want to look at the interaction of two prevalent software engineering approaches, namely \emph{Model Driven Engineering (MDE)} and \emph{Agile Software Development}.

MDE \cite{BrambillaCabotW2017, RODRIGUESDASILVA2015139} has been around for several years. 
The first tools supporting MDE appeared under the name Computer-Aided Software Engineering (CASE) in the 1980s.
A significant event within the history of MDE is denoted by the publication of the Unified Modeling Language (UML) \cite{OMG2015UML} through the Object Management Group (OMG) industrial consortium.
UML represents a standard for the creation of conceptual models describing the structure and behavior of complex system, which can serve as input artifacts for code generation, simulation and reasoning.
MDE has found a broad adoption in academia there is a plethora of material available about formal semantics, transformation and application of modeling.
In the industry MDE has found some application but is till far away to be the standard \cite{secondaryHutchinsonEmpirical, whittle2014state}.

Agile software development is an approach, which was coined by several practitioners in software engineering.
It was popularized by the \emph{Manifesto for agile software development} \cite{secondaryAgileManifesto}, which defines the values and principles of these approaches. 
There evolved different formally defined methodologies, e.\,g. Scrum, Kanban and eXtreme Programming (XP).
The core idea of this approaches is the emphasize on the flexibility of small individually acting teams, which incrementally produce executable software in short time intervals, so called iterations.
Such an approach is better suited to changing customer requirements then traditional plan-based approaches.

Some supporters of the Agile approach claim that MDE is as a lost cause \cite{2}. 
Therefore, we want to investigate the interaction of both approaches. 
Do they represent contradicting approaches or can they be combined and does this combination then yield a positive impact?
In this paper we conduct a literature review to discover published evidence of software engineering approaches combining both approaches and the respective experiences.

The structure of this paper is as follows.
In section~\ref{sec:method} we introduce our precise research questions and the method used to conduct the literature review.
Section~\ref{sec:survey} provides an overview of the discovered results from the review.
Finally section~\ref{sec:conclusion} draws a conclusion of the literature review and gives answers to the research questions from section~\ref{sec:method}.

\section{Method}
\label{sec:method}

@@

Answers to these questions will help us to understand, if both approaches to Software Engineering are used in combination in practice, if their combination yields positive effects and in which areas it is actually applied. 
To get profound results we are looking for peer-reviewed scientific publications published in journals or conferences. 
We decided incorporate the following databases for our search:
\begin{itemize}
\item ACM Digital Library
\item Google Scholar
\item IEEExplore
\item ScienceDirect
\end{itemize}

@@

The search yielded around thirty results in the ACM and IEEE library and more than 3000 results in the two other databases. 
We decided to restrict the time interval to papers after 2001 as the \emph{Agile Manifesto} \cite{secondaryAgileManifesto} was published in this year, which can be considered to be the beginning of the Agile movement.
To narrow the search further down, we defined the following inclusion criteria, which a search result has to fulfill to be considered in our survey:
\begin{description}
\item[Inclusion] conference or journal article, contains practical relevance, papers after 2001
\end{description}

We applied this criteria by looking at title and abstract of the discovered results. 
It turned out that most of the found papers did not contain Agile and MDE methodology at the same time.
Furthermore a lot of papers did not refer to any practical experiences.
After rigorously applying the filter criteria, we ended with 12 papers. 
For the analysis we did not apply a fixed review protocol due to the small number of findings and performed a free summary instead.
A survey about the discovered result is presented in the next section.

\section{Survey}
\label{sec:survey}

\subsection{Agile Model Driven Development}

For Scott W. Ambler \cite{1} modeling is an important part of all software development projects because it enables to think through complex issues before the attempt to address them via code. This is true for agile projects, for not-so-agile projects, for embedded projects, and for business application projects. Unfortunately, many modeling efforts prove to be dysfunctional. At one end of the spectrum there are projects where no modeling is performed, either because the developers haven’t any modeling skills or because they have abandoned modeling as a useless endeavor. At the other end of the spectrum there are projects which sink in a morass of documentation and overly detailed models, either because the project team suffers from “analysis paralysis” and finds itself unable to move forward or because the team has burdened itself with too many modeling specialists who don’t have the skills to move forward even if they wanted to. Somewhere in the middle, there are project teams that invest in modeling and documentation efforts only to discover that the programmers ignore the models anyway, often because the models are unrealistic or simply because the programmers think they know better than the modelers (and often they do). The goal of Agile Model Driven Development (AMDD) is to show how to avoid these problems, to gain the benefits of modeling and documentation without suffering the drawbacks.

AMDD as the agile version of MDD (Model Driven Development) takes a much more realistic approach in his opinion: its goal is to describe how developers and stakeholders can work together cooperatively to create models which are just barely good enough. It assumes that each individual has some modeling skills, or at least some domain knowledge, that they will apply together in a team in order to get the job done. It is reasonable to assume that developers will understand a handful of the modeling techniques out there, but not all of them. It is also reasonable to assume that people are willing to learn new techniques over time, often by working with someone else that already has those skills.

@@

Scott W. Ambler \cite{2} believes that modeling is a way to think issues through before the code step because it lets to think at a higher abstraction level. One can also do this by writing a test before writing functional code, along the lines of test-driven development.
With the Agile Model Driven Development (AMDD) approach, one typically just does enough high-level modeling at the beginning of a project to understand the scope and potential architecture of the system, and then during development, iteration modeling will be done as part of the iteration planning activities to. Lightweight models will be created in several minutes as precursor to several hours of coding.

@@

In the end of \cite{2} there is a discussion between Axel Uhl and Scott W. Ambler, Axel remarks some projects where MDA succeeded nevertheless Scott answers saying that he is not very excited about MDA due to big failures of some projects in the past.

@@

Matinnejad \cite{3} presents the concept of AMDD as an attempt to effectively bring together the fast pace of agile development and the guaranteed quality of model-driven development. This methodology makes use of the strong contrast between Agility and Model Driven Software Engineering or MDSE, attempting to cover each of their flaws with the strong points of the other, creating a symbiotic association. For instance, MDSE strict focus on documentation and models generation can supply perfectly the documentation “phobia” that suffers agile development.

@@

The final statement is that although AMDD is a promising field in a research and practical context, the author considers it not to be mature at all, stressing that it is still in its “infancy”. This paper can be used as an starting point in a AMDD research for creating, adapting or selecting AMDD processes.

@@

Karagiannis \cite{4} provides an overview on the practice of Agile Modeling Method Engineering (AMME). This practice mixes the use of modeling and agile methodologies, as a way to evolve modeling requirements all along the software life cycle and to connect more stakeholders and developers.

@@

Burden et.\,al. \cite{10} empirically investigate three companies, namely \emph{Ericson AB}, \emph{Volvo Cars} and \emph{Volvo Group}, which undergo a parallel shift to MDE and Agile Methods concerning their development methodologies.
They contribute to the broad empirical study by Hutchinson et. al. \cite{secondaryHutchinsonEmpirical} about the use of MDE in industry.
In general their observations validate the findings in \cite{secondaryHutchinsonEmpirical}., e.\,g. that MDE works best in narrow well-understood domains, it has to be driven bottom-up through developers and must be put on the critical path.
Though, they also refute some of the previous findings: 
Engineers are actually well-trained in MDE methodology by universities, code gurus appreciate code generators to reduce repetitive tasks, middle managers welcome MDE as it help minimizing risks and architects might find the complexity of MDE tools intimidating.
As a result Agile and MDE can yield synergies:
Agile profits from MDE by the enforced integration of stakeholders by abstracting away from the actual implementation. Furthermore it can reduce external dependencies because outsourced activities are brought back in-house through automation.
Finally the success from MDE can profit from the bottom-up approach of Agile Methods.
A further interesting finding of \cite{10} is the importance of secondary tools. 
As MDE tools can cause repetitive tasks, engineers naturally develop secondary tools, e.\,g. scripts to again automate this activities.

@@

In \cite{11} Kulkarni et.\,al. report about their experiences on the introduction of Agile Methods in a MDE based software development process within \emph{Tata Consultancy Services}.
This company is specialized on the delivery of E-commerce solutions for a wide range of customers from different areas.
As their customers require individual solutions but there is a big overlap between the requirements of the customers, MDE turned out to be very effective for them as a majority of an application can be generated and only minor adjustments are required.
The development of their MDE platform used to be based on a traditional plan-driven approach. 
When they changed to an agile approach, they first suffered a loss of productivity and estimations of cost and time were always wrong. 
After a few weeks, the process stabilized and they actually experienced an significant improvement of productivity and accuracy of estimates.
However, they experienced that a pure agile approach is not adequate for MDE, as sometimes in-depth analysis, exploration and research might be required in the development of the MDE tools.
As Agile promotes the delivery of executable artifacts and short timely intervals, these kinds of activities are barely feasible.
Therefore they adapted their approach by introducing Meta-Sprints, i.\,e. a longer sprint which is allowed to produce non-executable artifacts such as documentation, proof-of-concept prototypes etc.
Kulkarni et. al. report really positive experiences with this adapted agile approach.

@@

Golra et.\,al. \cite{12} report on their experience about using Agile Methods for the development of a graphical Domain Specific Language (DSL) in a project for a governmental organization in France.
In spite of defining the language top down with strict semantics, they developed the metamodel, the model and the graphical representations in parallel with loose coupling in between the artifacts.
They identified several positive finding on the effects of Agile within MDE.
In short Agile Methods within the development of graphical DSLs are a success story as they facilitate communication with domain experts and development teams.
Given flexibility both in tools and communication more accurate results can be achieved.
However, the authors point out that further conceptual studies in this area are required.

@@

In \cite{alfraihi2016towards} Alfahiri proposed series of publications that sets the stage for the research to be conducted by the authors. The author has identified gaps in the corpus of knowledge of the field of agile model driven development. He has identified gaps in 1) the understanding of the state of practice of agile model driven development 2) the benefits that agile MDD is supposed to provide and 3) identifying the challenges that beset the adoption of agile MDD.

The author begins by describing Model Driven Development as a new paradigm where models are the main artefact in software development and from which code is generated. He describes agile development as an approach that imposes a disciplined project management structure upon software development. To the author, both MDD and Agile methods share a core aim of accelerating the development process yet their approaches to achieve this aim are different.

@@

To the author, agile model driven development is an attempt to get the best of both paradigms while mitigating their drawbacks. To achieve this, significant research needs to be conducted to address the gaps identified. There is also a brief section on related work where a review of the current research in agile model driven development is presented. This literature review shows that most of the current work in the field is aimed at classifying how agile and MDD approaches are combined. The author points out that none of the published literature in the field addresses the questions of benefits and challenges of agile MDD \cite{matinnejad2011agile,stavru2013challenges,whittle2014state}.

@@

Matinnejad \cite{matinnejad2011agile} presented a case study where agile model driven development approaches are applied to the development of a real time telecommunications system at Motorola \cite{zhang2011agile}. In this case study, the investigators combined system-level agile process (SLAP) and an MDD process into one to speed up development rate, improve product quality and shorten delivery cycle time. SLAP is an agile process adopted at Motorola that uses scrum as a baseline and includes certain extreme programming practices. SLAP divides a software development life cycle into multiple iterations. Each iteration consists of three sprints: application requirements and architecture, development, and system integration feature testing (SIFT). Each sprint is five weeks long and has the same set of activities (called its calendar).

@@

@@

\begin{itemize}
\item \emph{Limited support for distributed development environments:} software. Documentation and models should be created and maintained only if they provide value to the project and project stakeholders. Otherwise, face-to-face communication is as important in distributed environments as the non-distributed environment.
\item \emph{Limited support for subcontracting:} The process may be an iterative, incremental approach, but the subcontractor may have to make the process predictive by specifying the number of iterations and the deliverables of each iteration in order to compete.
\item \emph{Limited support for building reusable artifacts:} While there seems to be a case for applying agile processes to the development of reusable artifacts, it is not clear how agile processes can be suitably adapted.
\item \emph{Limited support for development involving large teams:} There may be opportunities for teams to use agile practices, but the degree of agility possible may be less than that found in smaller projects.
\item \emph{Limited support for developing safety-critical software:} it can be assumed that agile and formal software development are not incompatible but can be combined when needed: Formal techniques may be used in an agile way to handle critical pieces of the software to increase quality and confidence.
\item \emph{Limited support for developing large, complex software:} The assumption that code refactoring removes the need to design for change may not hold for large complex systems in particular. The complexity and size of such software may make strict code refactoring costly and error-prone. Models can play an important role here, especially if tools exist for generating significant portions of the code from the models. This view of models as the central artifacts for evolving systems is at the heart of the Object Management Group’s (OMG) Model-Driven Architecture (MDA) approach.
\end{itemize}

@@

Two case studies where conducted on the engineering teams responsible for the clutch control for the electrical drivetrain in a hybrid vehicle and for the active high beam highlight. Both case studies implemented MDE and agile methods in the workflow. The studies indicate that the development cycle where shortened by implementing the new methods in the engineering teams, but that one of the biggest problem to address is the faulty plant models delivered from the third party vendors. The paper concludes with the statement that MDE and agile methods can successfully be combined to speed up the development phase of a software system in a car. With faster feedback methods from the agility framework, the developers were able to address holes in their knowledge and decrease the number of errors in their preliminary software. The paper also suggested more future work with MDE methods, and more automated code generation.

@@

Rivero et. al. \cite{RIVERO2014670} introduce a bottom-up driven approach on implementing model-driven web engineering. Instead of using the traditional top-down approach in model-driven engineering, where application content is modeled initially, the authors suggest to invert the development process and start with the user interface-mockups. From the mockups, code generation and model-driven engineering methods are used to build the actual functional software. By inverting the normal top-down approach normally found in MDE, the authors argue that the result is an agile prototype-based iterative process, with the advantages of automatic code-generation and documentation from MDE.

The paper concludes that their method reduces the errors and the effort in model construction, while at the same time allows introducing agile features to the modeling process. By generating code based on mockups, the authors method shows a fast and agile way of developing user friendly web application, where non domain-experts can create functional web design straight from their conceptualized mockups. For future work the authors will keep testing and validating the developed tool by using it to build applications. They are also extending the tool to provide code generation capabilities for common Web technologies and architectures.

\section{Conclusion}
\label{sec:conclusion}
This section summarizes the results of the survey and present the conclusion extracted.
Despite the survey covered the study of just 12 papers, good results and relevant information were found.
Still, a publication bias about the lack of possible publications about unsuccessful combinations of MDE and Agile has to be considered.

@@

Accordingly to the reports we found during the research, projects that eventually incorporated or followed, AMDD improved the results in some way.
The study case of Volvo Cars revealed that MDE and agile methods can successfully be combined to speed up the development phase of a software system in a car\cite{Eliasson2014}.
Rivero et. al. \cite{RIVERO2014670} showed that by generating code based on mockups, the authors method shows a fast and agile way of developing user friendly web application, where non domain experts can create functional web design straight from their conceptualized mockups.
The results in the case of Motorola \cite{zhang2011agile} declared that 93\% of the entire component code was automatically generated and the quality of this generated code in terms of defects density was significantly higher than manual code.
